\section{Introduction}
\label{sec:introduction}

The symmetric group \(\Sfour\) is small enough to permit complete finite replay over its 24 one-line words, but already rich enough to carry different structures on the same ambient labels. A subset of \(\Sfour\) may be studied as a set of words, as a set of local prefix flags, as a set of permutation-matrix supports, as a linear-extension set of a strict poset, or as a subgroup row. These viewpoints share an index set, but they do not preserve the same mathematical properties.

The purpose of this paper is to prove a controlled finite separation inside that layer. The main comparison is between exact poset-cone status, meaning \(X=\Lin(P)\) for a strict poset \(P\) on \([4]\), and subgroup-row status, meaning \(X\le \Sfour\) under the stated composition convention. The prefix-flag and permutation-matrix models provide the finite indexing dictionary; the selected data package provides bounded replay support for the rows and counts used in the argument. Finite certificates are used only for bounded replay claims. They do not replace the proof obligations for the structural lemmas.

External references are used below only for standard terminology around symmetric groups, posets, and linear extensions. The finite claims of this paper are the bounded \(\Sfour\) statements below.

The main contributions are as follows.

\begin{enumerate}[label=(\roman*)]
\item We fix the one-line \(\Sfour\) convention and prove the canonical bijection between words, local \(A_3\) prefix flags, and \(4\times4\) permutation-matrix supports.
\item We identify the \(A_3\) prefix-support vector of a subset \(X\subseteq \Sfour\) with the cardinalities of its unordered set-prefix shadows.
\item We prove that the common-precedence closure of a nonempty subset \(X\subseteq\Sfour\) is a strict poset and gives an exact criterion for whether \(X\) is a linear-extension set.
\item We use the locked \(\Dfour\), \(\Vfour\), and N-poset rows to show that exact poset-cone status is not equivalent to subgroup-row status on the displayed finite witnesses.
\item We record bounded package counts and replay checks accompanying the finite comparison, while separating the 219 distinct mathematical subset count from artifact-row counts.
\end{enumerate}

The scope is deliberately finite. The paper does not classify all \(2^{24}\) subsets of \(\Sfour\), does not prove an all-tiler theorem, and does not promote a geometric or general \(\Sn\) theorem. The selected comparison table is a witness table, not a full structural classification of the selected data package.